RickView: Lightweight Standalone Knowledge Graph Browsing

### 2024-03-22 paper.tex
more stats

\begin{table}
\begin{tabular}{lrrcSSSSS}
\toprule
% triples SNIK 44584, HITO, ANNO, linkedspending					
Knowledge Graph	&\textnormal{triples}		&\textnormal{N-Triples}	&\textnormal{HDT}	&\textnormal{LodView}	&\textnormal{Virtuoso}	&\textnormal{LodView+Virtuoso}	&\textnormal{RickView}\\
\midrule
SNIK	 		&45\,k~						&2.0\,MiB				& ---				&561					&207					&767							&23.4\\
HITO 			&14\,k~						&1.0\,MiB				& ---				&553					&121					&674								&18.2\\
ANNO			&30\,k~						&3.5\,MiB				& ---				&						&						&								&22.3\\
Ruthes			&15\,M						&3.7\,GiB				&146\,MiB			&						&						&								&203.4\\
LinkedSpending	&1350\,M					&28.2\,GiB				&1.4\,GiB			&						&						&								&1975.3\\
\bottomrule
\end{tabular}
\label{tab:stats}
% todo correct versions
\caption{Knowledge graph serialized size (uncompressed N-Triples) and total deployment RAM consumption of LodView 1.2.3, Virtuoso 7.2.12 and RickView 0.2.13 of SNIK v24.03, HITO v24.02, ANNO v24.02 and LinkedSpending v2015.
LinkedSpending uses the compressed HDT mode, see \cref{sec:hdt}.
%File sizes and memory usage in MiB rounded to one decimal place.
}
\end{table}

>>>>

\begin{table}
\begin{tabular}{lrrcSSSSS}
\toprule
% triples SNIK 44584, HITO, ANNO, linkedspending					
Knowledge Graph	&\textnormal{triples}		&\textnormal{N-Triples}	&\textnormal{HDT}	&\textnormal{LodView}	&\textnormal{Virtuoso}	&\textnormal{LodView+Virtuoso}	&\textnormal{RickView}\\
\midrule
SNIK	 		&45\,k~						&2.0\,MiB				& ---				&561					&207					&767							&23.4\\
HITO 			&14\,k~						&1.0\,MiB				& ---				&553					&121					&674							&18.2\\
ANNO			&30\,k~						&3.5\,MiB				& ---				&						&						&								&22.3\\
Ruthes			&15\,M						&3.7\,GiB				&146\,MiB			&						&						&								&203.4\\
LinkedSpending	&1350\,M					&28.2\,GiB				&1.4\,GiB			&539					&290--4077				&829--4606						&1975.3\\
\bottomrule
\end{tabular}
\label{tab:stats}
% todo correct versions
\caption{Knowledge graph serialized size (uncompressed N-Triples) and total deployment RAM consumption of LodView 1.2.3, Virtuoso 7.2.12 and RickView 0.2.13 of SNIK v24.03, HITO v24.02, ANNO v24.02 and LinkedSpending v2015.
LinkedSpending uses the compressed HDT mode, see \cref{sec:hdt}.
%File sizes and memory usage in MiB rounded to one decimal place.
}
\end{table}
